---
title: "Lab 03"
author: "Hanin Alzaher"
date: ""
editor_options: 
  chunk_output_type: console
output:
  pdf_document: default
---

# Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(sf)
``` 

# Data

```{r load-data, message = FALSE}
fl_votes <- st_read("data/fl_votes.shp", quiet = TRUE)
fl_votes %>%
  slice(1:6)
```


# Exercise 1

```{r add-winner}
fl_votes <- fl_votes %>%
  mutate(winner20 = if_else(rep20 > dem20, 'Donald Trump', 'Joe Biden'))
```


# Exercise 2

```{r fl-plot-1}
ggplot(fl_votes) + geom_sf(aes(fill=winner20)) + 
  scale_fill_manual(values = c("#DE0100" , "#0015BC")) +
  labs(title = "Election winner 2020", fill = "winner") +
  theme_bw()

```

# Exercise #3

```{r fl-props}
fl_votes <- fl_votes %>%
  mutate(prop_rep16= rep16/(rep16+dem16), prop_rep20= rep20/(rep20+dem20))
```

# Exercise 4

```{r fl-plot-2}
ggplot(fl_votes) + geom_sf(aes(fill = prop_rep20)) +
  scale_fill_gradient(low = "#0015BC", high = "#DE0100" ) +
  labs(title = "Election 2020 Results", fill = "Republican share of votes") +
  theme_bw()
```

# Exercise 5

```{r fl-change}
fl_votes <- fl_votes %>%
  mutate(diff_rep = prop_rep20 - prop_rep16)
```

# Exercise 6

```{r fl-plot-3}
ggplot(fl_votes) + geom_sf(aes(fill = diff_rep)) +
  scale_fill_gradient2(low = "#0015BC" , high = "#DE0100") +
  labs(title = "Election 2016 and 2020 results", fill = "Change in Republican share") +
  theme_bw()
```

# Exercise 7

What do the visualizations you developed tell you about the 2016 and 2020 Presidential election in Florida? What are limitations of these visualizations?

The visualizations show that Donald Trump won the with the majority of votes in Florida state. The limitation we faced is the plot in exercise 2 was not clear.
  

